Dobbs' Decision And Abortion2

### 2025-01-15 ProjectBlog/others/Ipynb/ipynb.qmd
Dobbs' Decision And Abortion2

---
title: "Dobbs' Decision And Abortion"
date: 01/05/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
    default-image-extension: svg
bibliography: references.bib
---

>>>>

---
title: "Dobbs' Decision And Abortion2"
date: 01/05/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
    default-image-extension: svg
bibliography: references.bib
---
